Partitioning mortality into growth-dependent and growth-independent hazards across 203 tropical tree species

### 2018-11-03 ms/manuscript.Rnw
minor typo

\documentclass[9pt,twocolumn,twoside, lineno]{pnas-new}\usepackage[]{graphicx}\usepackage[]{color}

@@

\affil[a]{Department of Biological Sciences, Macquarie University, Sydney, NSW, 2109, Australia}
\affil[b]{Field Museum of Natural History, Chicago, IL, 60605, United States of America}
\affil[c]Morton Arboretum, Lisle, IL ,60532, United States of America}
\affil[d]{Data61, Commonwealth Scientific and Industrial Research Organisation (CSIRO), Sydney, NSW, 2015, Australia}
\affil[e]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[f]{Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, 2052, Australia}

@@

\acknow{We thank H. Muller-Landau and anonymous reviewers for feedback and B. Carpenter for technical advice. We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. Fig. 1b uses images by Tracey Saxby, IAN Image Library. J.S.C., R.G.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.S.F. and M.W. were supported by fellowships from the Australian Research Council.}

>>>>

\documentclass[9pt,twocolumn,twoside]{pnas-new}\usepackage[]{graphicx}\usepackage[]{color}

@@

\affil[a]{Department of Biological Sciences, Macquarie University, Sydney, NSW, 2109, Australia}
\affil[b]{Field Museum of Natural History, Chicago, IL, 60605, United States of America}
\affil[c]{Morton Arboretum, Lisle, IL ,60532, United States of America}
\affil[d]{Data61, Commonwealth Scientific and Industrial Research Organisation (CSIRO), Sydney, NSW, 2015, Australia}
\affil[e]{Smithsonian Tropical Research Institute, Apartado 0843–03092, Balboa, Panama}
\affil[f]{Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, 2052, Australia}

@@

\acknow{We thank H. Muller-Landau, Peter Vesk and anonymous reviewers for feedback and B. Carpenter for technical advice. We acknowledge S. Hubbell, R. Foster, R. Pérez, S. Aguilar, S. Lao, S. Dolins, \& hundreds of field workers for their contribution; and the National Science Foundation, Smithsonian Tropical Research Institute, \& MacArthur Foundation for funding the design, collection, quality control and management of long-term growth data at BCI. J.S.C., R.G.F., L.M. and D.S. were supported by the Science and Industry Endowment Fund (SIEF; RP04-174). D.S.F. and M.W. were supported by fellowships from the Australian Research Council.}
